Maaslin runs

### 2019-06-12 maaslinruns.Rmd
Duplicated labels

```{r read combinations, eval = TRUE}
ret3rd <- lapply(var.CL.comb3rd, function(x) {
    file <- sprintf("/homes/jpalmu/maaslinruns/maaslinruns/1560338417_%s/maaslin/maaslin.txt",
                    paste0(x, collapse = "_"))
    read.table(file, header=TRUE, sep='\t') %>% as.data.frame
    })
```

```{r combine results}
ret3rd.comb <- map_df(ret3rd, ~as.data.frame(.x), .id="id")

>>>>

```{r read combinations 3rd, eval = TRUE}
ret3rd <- lapply(var.CL.comb3rd, function(x) {
    file <- sprintf("/homes/jpalmu/maaslinruns/maaslinruns/1560338417_%s/maaslin/maaslin.txt",
                    paste0(x, collapse = "_"))
    read.table(file, header=TRUE, sep='\t') %>% as.data.frame
    })
```

```{r combine results 3rd}
ret3rd.comb <- map_df(ret3rd, ~as.data.frame(.x), .id="id")
